sensiAnPaper1All

### 2015-07-01 sensiAnPaper1All.Rmd
deleted post processing function and code moved into Rmd instead

@@

### now want to calculate the times to reach critical points and add them on to the input file 
### for different scenarios
### or will sensiPostProc() sort that ?

  ## post processing
  #sensiPostProc( inAndOutMix = inAndOutMix,
  #               inAndOutI1 = inAndOutI1,
  #               inAndOutI2 = inAndOutI2 )

>>>>

The main question is under which scenarios are mixtures better than sequential ?

This breaks down into these subsidiary quetsions :
1. Under which scenarios is the time to resistance for either insecticide quicker for

@@

### now want to calculate the times to reach critical points and add them on to the input file 
### for different insecticide strategies, sequential, mix1 and mix2
```{r}
  #1) sequential : time to resistance for each insecticide in isolation
  #inputs : inAndOutI1, inAndOutI2
  #find time to criticalPoint for insecticide1
  #find time to criticalPoint for insecticide2
  #add together
  resistPoints1 <- findResistancePoints(listOutI1, locus=1)
  resistPoints2 <- findResistancePoints(listOutI2, locus=2)

  resistPointsSeq <- resistPoints1 + resistPoints2

  #2) mixture1 : time to resistance for either insecticide when used in a mixture
  #inputs : inAndOutMix
  #find time to criticalPoint for EITHER insecticide in mixture  
  resistPointsMix1 <- findResistancePoints(listOutMix, locus='either')  
  #todo - to be comparable I think this should be for when resistance to BOTH insecticides is reached

  #3) mixture2 : when resistance to one insecticide in the mixture reached, switch to sole use of the 
  #   other until that too reaches the critical point. Record total time.
  # what I actually need to do is start with mixture find the first critical point
  # (need to know which of the insecticides it is)
  # then I need to go to the single run for the other insecticide & starting at 
  # it's current resistance point find out how many more generations to go
  #inputs : inAndOutI1, inAndOutI2, inAndOutMix

  #resistPointsMix2 <- findResistancePointsMixResponsive(listOutMix, listOutI1, listOutI2)
```

### calculate the difference between sequential & mixture scenarios
```{r}

  # easy to calc for which scenarios mixture1 is 'better' i.e. longer to resistance
  #boolean
  resistBetterMix1SeqBoolean <- resistPointsMix1 > resistPointsSeq
  #converted to 0/1
  resistBetterMix1Seq <- plyr::aaply(resistBetterMix1SeqBoolean,.margins=c(1,2),.fun=as.numeric)
  #rename rows ready for binding on to inputs
  rownames(resistBetterMix1Seq) <- gsub('gen','betterMix1Seq', rownames(resistBetterMix1Seq))

```

### here I want a file with the inputs (just one value for exposure)
### with extra columns for seq
```{r}
treeInput <- rbind( listOutMix$input, resistBetterMix1Seq )

```
